\chapter{Introduction}
\label{chap:intro}
Text 1

Text 2

Text 3

\section{Background and Motivation of Thesis} \label{sec:i1}

Mobile applications are the new hype since the launch of the first iPhone generation on 2007. The market of mobile application was grown extremely fast and the variety of applications also. The next trend will be location-based service, mobile search, mobile payment and mobile social networking. Hybrid applications could be one way to develop applications with these services. It is easy to design with a application with HTML and JavaScript and the biggest benefit is, the easy way to deploy the app on different platforms
and devices. The new technologies HTML5 will bringing new features to the devices and hybrid applications will relay benefit from that. This thesis will introduce into hybrid
technology and will show you the opportunities with a prototype.

\section{Project Objectives}\label{sec:i2}
% Reference to Section \ref{sec:i1}, and reuse of \ac{ac} nad \ac{ac2} with also full use of \acf{ac2}. 
Text 1

Text 2

Text 3

\subsection{Significance of the Project}\label{sec:i2.1}
Text 1

Text 2

Text 3

\subsection{Significance of the Problem}\label{sec:i2.2}
Text 1

Text 2

Text 3

\subsection{Research Objectives}\label{sec:i2.3}
What is the State of Art in Mobile Application development?
What is the Future in Mobile Application market?
Which is the best design process to follow?
Which design pattern to follow?
What is the best Mobile Platform to use? 

\section{Definition of terms}\label{sec: i3}
Text 1

Text 2

Text 3

\section{Thesis Structure}\label{sec: i4}
% Reference to Chapter \ref{chap:intro}, and reuse of \ac{GUC} with also full use of \acf{DHBW}. \ref{subsec:i1}
Text 1

Text 2

Text 3